MADA Data Analysis Project

### 2021-11-28 code/analysis_code/04-Mods.P2.BestTree.rmd
Confirmed analysis output knits

```{r}
rpart.plot(extract_fit_parsnip(best_tree_fit)$fit)
```

```{r}
#predicted versus observed
plot(tree_pred$.pred,train_data$Ct, xlim =c(0,100), ylim=c(0,100))
abline(a=0,b=1, col = 'red') #45 degree line, along which the results should fall

>>>>

```{r}
rpart.plot(extract_fit_parsnip(best_tree_fit)$fit, tweak = 1.2)
```

```{r}
#predicted versus observed
plot(tree_pred$.pred,train_data$Ct)
abline(a=0,b=1, col = 'red') #45 degree line, along which the results should fall

### 2021-11-28 products/manuscript/Manuscript.Rmd
Confirmed analysis output knits

processing script.R was modified to do initial cleaning and preparation of the data set for further exploration.

@@

This can be found in processing_code/ProcessingScript.RMD

@@

Direction was influenced by [@Weir2016-sj] on "Effect fo Surface Sampling and Recovery of Viruses and No-Spore-Forming Bacteria on a Quantitative Microbial Risk Assessment Model for Fomites".

@@

Tool A has an average Ct recovery higher than B. This makes sense as the surfaces A recovered from is 2 logs higher (-1) than that of B (-3). A log drop is \~3Ct values we can see from the graphic that it trends as predicted. Suggests that

>>>>

`processing script.R` was modified to do initial cleaning and preparation of the data set for further exploration.

@@

This can be found in `processing_code` folder in repository that generate rds files located in the `data/processed_data` folder.

@@

Processed data

@@

Tool A has an average Ct recovery higher than B. This makes sense as the surfaces A recovered from is 2 logs higher (-1) than that of B (-3). A log drop is \~3Ct values we can see from the graphic that it trends as predicted. Suggests that
```{r P2-Tool-AB-Sum, eval=FALSE, fig.cap="Phase", include=FALSE}
knitr::kable(table, caption= "Example Table Caption", digits=2, col.names = )
```
